Robots Showing Emotions: Emotion Representation with no bio-inspired Body

### 2016-10-30 JournalInteractionStudies/Parts/conclusions.tex
Changes in some parts of the article, main changes are described in Rebuttal2.txt

	\item Using a real platform to perform the case studies increases the enthusiasms of the participants and possibly their willingness to participate in the study. Although we did not evaluate directly this item during our case studies, it was observed during the set up that people were curious to see the robot moving. Also, during the pilot two kids had a different reaction when the robot was getting close to them. One of them was scared of the robot, while the other was curious about the robot.

@@

Further work should be done to understand how the combination of changes in the body shape could contribute to the expression of emotions. It is also necessary to recreate a simple scene to give the context to the participants, but this time just using two robots. This will eliminate possible clues that could be given by the human actor.

>>>>

	\item Using a real platform to perform the case studies triggers the enthusiasm of participants and, possibly, their willingness to participate in the study. Although we did not evaluate directly this item during our case studies, it was observed during the set up that people were curious to see the robot moving. Also, during the pilot two kids had a different reaction when the robot was getting close to them. One of them was scared of the robot, while the other was curious about the robot.

@@

Further work should be done to understand how the combination of changes in the body shape could contribute to the expression of emotions. It is also necessary to recreate a simple scene to give the context to the participants, but this time just using two robots. This could eliminate possible clues that could be given by the human actor.

### 2016-10-30 JournalInteractionStudies/Parts/introduction.tex
Changes in some parts of the article, main changes are described in Rebuttal2.txt

The expression of emotion in robots is becoming a quite important issue to implement robots able to interact with people in a social context. Following the results obtained by studying emotion expression in humans (e.g., \cite{Venture2014,Ekman2004}), it is possible to notice that most of the works focus on facial expressions (e.g.,~\cite{Breazeal2002}) or on humanoid poses (e.g.,~\cite{Canamero2010}), while the vast majority of robots on the market nowadays are not provided with face, arms and legs. Moreover, the focus is often on the position of limbs, or face elements, more than on the kind of movement that could express emotion, resulting on emotion expressions that could not be broadly used in most platforms.
There are applications where the shape of the robot is constrained by functional needs, such as in the case of home cleaners, lawn mowers, transporters, flying drones, and many others. In all these cases, emotions can be expressed with the only available body, exploiting movement features.

@@

The obtained results enable to say that it is possible to design movements, even for a neutral platform, that could be interpreted as emotional expression, with some differences among emotions, as confirmed also by other experiments~\cite{Sharma2013}.

@@

This paper is organized as follows. The next section provides a brief overview of relevant work related to emotion expression in robots. Section system outlines the platform used in the case studies. The section case studies presents the design and results for all four case studies.

>>>>

The expression of emotion in robots is becoming a quite important issue to implement robots able to interact with people in a social context. Following the results obtained by studying emotion expression in humans (e.g., \cite{Venture2014,Ekman2004}), it is possible to notice that most works focus on facial expressions (e.g.,~\cite{Breazeal2002}) or on humanoid poses (e.g.,~\cite{Canamero2010}), while the vast majority of robots on the market nowadays are not provided with face, arms and legs. Moreover, the focus is often on the position of limbs, or face elements, more than on the kind of movement that could express emotion, resulting on emotion expressions that could not be broadly used in most platforms.
There are applications where the shape of the robot is constrained by functional needs, such as in the case of home cleaners, lawn mowers, transporters, flying drones, and many others. In all these cases, emotions can be expressed with the only available body, exploiting movement features.

@@

The obtained results enable to say that it is possible to design movements, even for a neutral platform, that could be interpreted as emotional expression, with some differences among emotions, as confirmed also by other experiments in robotics~\cite{Sharma2013} and suggested by psychologist~\cite{Russell2003}.

@@

This paper is organized as follows. The next section provides a brief overview of relevant work related to emotion expression in robots. Section~\ref{sec:robotic_platform} outlines the platform used in the case studies. Section~\ref{sec:cases} presents the design and results for all four case studies.

### 2016-10-30 JournalInteractionStudies/Parts/system.tex
Changes in some parts of the article, main changes are described in Rebuttal2.txt

The system used in the case studies here reported has been developed to support the identification of features that could be used to project emotions with a non-bio-inspired platform. This system is composed of two complementary parts: robotic platform and emotional enrichment system. The platform has been envisioned to be as simple as possible without any resemblance to human-like embodiment, while the emotional enrichment has been designed to be applied also to other platforms and to be extended to other emotion expressions.

@@

This prototype was modified after the first experiments to improve the expressiveness of the upper part. Two additional servo motors and a mechanical structure to support all these motors were added. The two motors attached to beams could be controlled to obtain an asymmetric or opening-closing movement. 
The third motor deforms the upper part of the foam. Figure~\ref{fig:triskar-first-design} shows the placement of the motors. To hide the structure, foam and a light blue cloth covering the foam were used, as it could be seen in Figure~\ref{fig:triskar-cover}. The light blue color was selected because it is not expected to generate any particular arousal in people~\cite{Promarker}.

Although this version showed the possibility to convey emotions, still it was not autonomous enough to host the emotional enrichment system. Therefore, an Odroid-U3 microcomputer was added, communicating with Arduino Mega via ROS-Serial.
Also, it was decided to make some improvements in the upper part. Two reasons motivated this changes. First the deformation system was not changing the shape enough to be clearly perceived by subjects; second, the beams were damaging the foam. Therefore, a lever  was added to the deformation motor, and a piece of rubber was adopted to safely connect the beams with the foam. The final arrangement is shown in Figure~\ref{fig:triskar-second-design}.

>>>>

The system used in the case studies here reported has been developed to support the identification of features that could be used to project emotions with a non-bio-inspired platform. This system is composed of two complementary parts: robotic platform and emotional enrichment system. The platform has been envisioned to be as simple as possible without any resemblance to anthropomorphic embodiment, while the emotional enrichment has been designed to be applied also to other platforms and to be extended to other emotion expressions.

@@

This prototype was modified after the first experiments to improve the expressiveness of the upper part. Two additional servo motors and a mechanical structure to support all these motors were added. The two motors attached to beams could be controlled to obtain an asymmetric or opening-closing movement. 
The third motor deforms the upper part of the foam. Figure~\ref{fig:triskar-first-design} shows the placement of the motors. To hide the structure, foam and a light blue cloth covering the foam were used, as it could be seen  in Figure~\ref{fig:triskar-cover}. The light blue color was selected because it is not expected to generate any particular arousal in people~\cite{Naz2012}.

Although this version showed the possibility to convey emotions, still it was not autonomous enough to host the emotional enrichment system. Therefore, an Odroid-U3 microcomputer was added, communicating with Arduino Mega via ROS-Serial.
Also, it was decided to make some improvements in the upper part. Two reasons motivated these changes. First the deformation system was not changing the shape enough to be clearly perceived by subjects; second, the beams were damaging the foam. Therefore, a lever  was added to the deformation motor, and a piece of rubber was adopted to safely connect the beams with the foam. The final arrangement is shown in Figure~\ref{fig:triskar-second-design}.
